\thema

### 2019-09-10 Docs/paper/report.tex
English text in paper; rebuilt PDFs
Rebuilt pdf
Corrected text
Paper update

\reporttypetext{Teamprojekt (Master 3. Semester)}

@@

\makecover[]
%          
%% Include an optional title page.
%\input{title}

@@

The predicted values are very close to the label for a difference of only 5 minutes to the input data. The further the time progresses, the worse the prediction becomes.
In the last image it looks like the resolution of the output has been drastically decreased compared to the first output. 
In fact the resolution is the same we can say that this is an indication of uncertainty in the Network.
Over the time, the movement of the rainfall is well predicted. even the tiny spot in the top left of Images can be predicted.
Even if the area of rainfall increases much faster than in the labels, the center is still well predicted and close to the center of the label.

\section*{Classification}
The second approach is to predict the precipitation by classification. Here we try to classify into either three classes (no rain, rain, heavy rain) or two classes (no rain, rain) for each pixel.
Herefore the Unets output is modified to three classes per pixel and an additional softmax layer at the output to provide propabilities. The labels are generated by a threshold for each class.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{../pics/categorical_crossentropy_hidden-softmax_output-softmax_above_3072}
\caption{classification output. in the left image the prediction of the first class (no rainfall) is plotted. The white spots are 100\% no rainfall. the black spots are 0\% no rainfall.}
\end{figure}

The gray spots can be rainfall or not depending on the propability of the other two classes. The right image (difference) shows us the absolute difference between the prediction and the label.
Here we can see that the big black spots (no difference between prediction and label) are at the no rainfall labels. This can be explained later. 
The network has a high accuracy by predicting rainfree pixels. this can be shown in the follwing ROC-image. 
By evaluating the confusion matrix for three class classification, you can recognize that the last class (heavy rainfall) is higly undersampled. 
There are much more rainfall pixels and even more no rainfall pixels in the dataset. To increase the the performance we tried over and undersampling, but both tecniques didnt work well for our scenario.
Finally we changed the problem to a two clas classification with a threshold of 0, so the classes are 'no rainfall' and 'rainfall'.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{../pics/roc-curve-RESIZED_TXT}
\caption{The ROC shows the performance by classification. The calculated AUC is close to 97\%, wich means, that the model has a good class separation.}
\end{figure}

\section*{Conclusion and Future Work}
In summary, this paper argued that short term precipitation prediction can be done by only observing radar data and without any other source of information.
The accuracy could still be imporved as well at the regression, were another lossfunction may could help, as at the classification were the 'rainfall' class is still undersampled and worse accurate than the 'no rain' class.

>>>>

\reporttypetext{Teamproject (Master 3. semester)}

@@

\makecover[]

@@

The predicted values are very close to the label for a difference of only 5 minutes to the input data. The further the time progresses, the worse the prediction becomes.
In the last image it looks like the resolution of the output has been drastically decreased compared to the first output. 
In fact the resolution is the same we can say that this is an indication of uncertainty in the Network.
Over time, the movement of the rainfall is well predicted. Even the tiny spot in the top left of images can be predicted.
Even if the area of rainfall increases much faster than in the labels, the center is still well predicted and close to the center of the label.

\section*{Classification}
The second approach is to predict the precipitation by classification. Here we try to classify into either three classes (no rain, rain, heavy rain) or two classes (no rain, rain) for each pixel.
Therefore the Unets output is modified to three classes per pixel and an additional softmax layer at the output to provide propabilities. The labels are generated by a threshold for each class.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{../pics/categorical_crossentropy_hidden-softmax_output-softmax_above_3072}
\caption{Classification output. In the left image the prediction of the first class (no rainfall) is plotted. The white spots are 100\% no rainfall. The black spots are 0\% no rainfall.}
\end{figure}

The gray spots can be rainfall or not depending on the propability of the other two classes. The right image (difference) shows us the absolute difference between the prediction and the label.
Here we can see that the big black spots (no difference between prediction and label) are at the no rainfall labels.
The network has a high accuracy by predicting rainfree pixels. This can be shown in the follwing ROC-image. 
By evaluating the confusion matrix for three class classification, you can recognize that the last class (heavy rainfall) is higly undersampled. 
There are much more rainfall pixels and even more no rainfall pixels in the dataset. To increase the the performance we tried over and undersampling, but both techniques didnt work well for our scenario.
Finally we changed the problem to a two clas classification with a threshold of 0, so the classes are 'no rainfall' and 'rainfall'.

The ROC-curve in figure~\ref{fig:roc} shows how well the two classes rain and no rain can be separated and predicted independent of the number of elements per class.

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{../pics/roc-curve-RESIZED_TXT}
\caption{The ROC shows the performance by classification. The calculated AUC is close to 97\%, wich means, that the model has a good class separation.}
\label{fig:roc}
\end{figure}

\section*{Conclusion and Future Work}
In summary, this paper argued that short term precipitation prediction can be done by only observing radar data and without any other source of information.
The accuracy could still be improved as well at the regression, were another lossfunction may could help, as at the classification were the 'rainfall' class is still undersampled and worse accurate than the 'no rain' class.
